Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-03-01 scripts/04_downstream_analysis.Rmd
ENH small fixes and enhancements
ENH running GO term enrichment only on three clusters, but on the three ontologies

```{r}
library(biomaRt)
ensembl = useMart("ensembl")
ensembl = useDataset("mmusculus_gene_ensembl", mart=ensembl)
```

```{r enrichment_analysis, results="hide"}
clusters = sort(as.vector(unlist(unique(labels))))
all_pathways = data.frame()
for(cluster in clusters){
    genes = gene_names[labels == cluster]

@@

```{r go_term_enrichment}

```

>>>>

```{r results="hide"}
library(biomaRt)
ensembl = useMart("ensembl")
ensembl = useDataset("mmusculus_gene_ensembl", mart=ensembl)
```

```{r enrichment_analysis, results="hide", message=FALSE}
clusters = sort(as.vector(unlist(unique(labels))))
clusters = c(1, 2, 3)
all_pathways = data.frame()
for(cluster in clusters){
    genes = gene_names[labels == cluster]

@@

To find GO terms, we use `biomaRt` to find the mapping between GO terms and
gene mapping.

```{r go_to_gene_mapping, results="hide", message=FALSE}

genes = getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

# Create gene to GO id mapping
gene_id_go_mapping = NULL
i = 1
for(gene in gene_names){
    go_terms = genes[genes[, "refseq_mrna"] == gene, "go_id"]
    if(length(go_terms) != 0){
        gene_id_go_mapping$gene = go_terms
	names(gene_id_go_mapping)[i] = gene
	i = i + 1
    }
}
```

```{r go_term_enrichment, results="hide", message=FALSE}
source("GO_terms_analysis.R")

all_go_terms = data.frame()
for(cluster in clusters){
    for(ontogoly in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

	if((dim(all_go_terms)[1] == 0) & (dim(go_terms_enriched)[1] != 0)){
	    go_terms_enriched["Cluster"] = cluster
	    go_terms_enriched["Ontology"] = ontology
	    all_go_terms = go_terms_enriched
	}else if(dim(go_terms_enriched)[1] != 0){
	    go_terms_enriched["Cluster"] = cluster
	    go_terms_enriched["Ontogoly"] = ontology
	    all_go_terms = merge(all_go_terms, go_terms_enriched, all=TRUE)
	}
    }
}
```

```{r echo=FALSE}
library(kableExtra)

all_go_terms = all_go_terms[
    order(all_go_terms[, "Cluster"],
	  all_go_terms[, "resultFisher_padj"]), ]

kable(all_go_terms, "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```
